---
title: "Ticker Univariate Analysis"
#output: html_notebook
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  html_document:
    toc: true
    number_sections: true
---

```{r seetup, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE, results='hide', comment=NA}
setwd("/cloud/project")
options(scipen = 999)
now<-format(Sys.time(), "%d-%m-%Y")
```

```{r ticker, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE, results='hide', comment=NA}
stock <- 'HTZ'
```
## Data Results{.tabset}

### Historic Data Table
```{r get data, message=FALSE, warning=FALSE, comment=NA, include=FALSE, paged.print=FALSE, results='hide'}
require(quantmod)
start <- Sys.Date() - 1092
end <- Sys.Date()
tickers <- c(stock)
data <- NULL
for(ticker in tickers)
  data <- na.omit(cbind(data,getSymbols(ticker, from = start, to = end,auto.assign = F)))
rm('tickers', 'ticker')
names(data) <- c("open","high", "low", "close", "volume","adjusted")
hist <- round(data,2)
hist
write.csv(hist, file=paste("/cloud/project/", stock, "_hist_", now,".txt", sep=""))
```

```{r describe historic data, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, comment=NA}
require(Hmisc)
describe(hist)
```

### YTD Data

```{r YTD, message=FALSE, warning=FALSE, comment=NA, include=FALSE, paged.print=FALSE}
ytd <- data["2019-01-01/"]
ytd
write.csv(ytd, file=paste("/cloud/project/", stock, "_ytd_", now,".txt", sep=""))
```

```{r describe ytd data, echo=FALSE, message=FALSE, warning=FALSE, comment=NA, paged.print=FALSE}
require(Hmisc)
describe(ytd)
```

## OHLC Analysis {.tabset}

### Highest and Lowest Points
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
# cat("Does the data contain at least OHL and C?") 
# is.OHLC(ytd) 
# cat("Does the data contain volume?") 
# has.Vo(ytd) 
# cat("just the Open column please.") 
# Op(ytd) 
cat("Where and what was the high point?")
cat("\n")
seriesHi(ytd) 
cat("\n")
cat("Where and what was the lowest point?")
cat("\n")
seriesLo(ytd)
```

```{r Create dataframes for percent changes echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
OpCl <- OpCl(ytd)
#OpCl

OpOp <- OpOp(ytd) 
#OpOp

HiCl <- HiCl(ytd)
#HiCl

```

```{r combined percent changes, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
percent_cbind <- cbind(ytd[,"adjusted"], OpCl, OpOp, HiCl)
percent_cbind  <- as.data.frame(percent_cbind)
names(percent_cbind) <- c("Adjusted","Daily Percent Change Open to Close","One Period Open to Open Change", "Percent Change High to Close")

percent_cbind <- cbind(Date = rownames(percent_cbind), percent_cbind)
rownames(percent_cbind) <- 1:nrow(percent_cbind)
#percent_cbind
write.csv(percent_cbind, file=paste("/cloud/project/", stock, "_percent_chng_", now,".txt", sep=""))
```

### Daily Percent Change Open to Close

```{r combined percent changes OpCl, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
plot(OpCl$OpCl.ytd, type = "l", col = "blue", lwd = 2, 
     ylab = "Percent Change", main = "Daily Percent Change Open to Close")

legend(x = 'topleft', legend = stock, lty = 1, lwd = 2, col = 'blue')

jpeg(file = "OpCl_line_chart.jpg")
dev.off()
```

### One Period Open to Open Change
```{r combined percent changes OpOp, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
plot(OpOp$OpOp.ytd, type = "l", col = "blue", lwd = 2, 
     ylab = "Percent Change", main = "One Period Open to Open Change")

legend(x = 'topleft', legend = stock, lty = 1, lwd = 2, col = 'blue')

jpeg(file = "OpOp_line_chart.jpg")
dev.off()
```

### Percent Change High to Close
```{r combined percent changes HiCl, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
plot(HiCl$HiCl.ytd, type = "l", col = "blue", lwd = 2, 
     ylab = "Percent Change", main = "Daily Percent Change Open to Close")

legend(x = 'topleft', legend = stock, lty = 1, lwd = 2, col = 'blue')

jpeg(file = "HiCl_line_chart.jpg")
dev.off()
```

## Chart Visualizations {.tabset}

### Monthly Closing Prices

```{r Monthly Closing Price, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
plot(ytd$adjusted, type = "l", col = "blue", lwd = 2, 
     ylab = "Adjusted close", main = "Monthly closing price")

legend(x = 'topleft', legend = stock, lty = 1, lwd = 2, col = 'blue')
```


### 10 Days Candle Stick Chart

```{r 10 Days candle stick chart, echo=FALSE, message=FALSE, warning=FALSE, comment=NA}
require(quantmod)

cat(("10 Days Candle Chart plus Technicals"),'\n')
candleChart(data,subset='last 10 days', multi.col=TRUE,theme='white',TA="addVo();addBBands();addEMA();addSMA(); addRSI()") 
```

### 1 Month Candle Stick Chart

```{r 1 Month candle stick chart, echo=FALSE, message=FALSE, warning=FALSE, comment=NA}
require(quantmod)

cat(("1 Month Candle Chart plus Technicals"),'\n')
candleChart(data,subset='last 1 months', multi.col=TRUE,theme='white',TA="addVo();addBBands();addEMA();addSMA(); addRSI()") 
```

### 2 Month Candle Stick Chart

```{r 2 Month candle stick chart, echo=FALSE, message=FALSE, warning=FALSE, comment=NA}
require(quantmod)

cat(("2 Month Candle Chart plus Technicals"),'\n')
candleChart(data,subset='last 2 months', multi.col=TRUE,theme='white',TA="addVo();addBBands();addEMA();addSMA(); addRSI()") 
```

### 3 Month Candle Stick Chart

```{r 3 Month candle stick chart, echo=FALSE, message=FALSE, warning=FALSE, comment=NA}
require(quantmod)

cat(("3 Month Candle Chart plus Technicals"),'\n')
candleChart(data,subset='last 3 months', multi.col=TRUE,theme='white',TA="addVo();addBBands();addEMA();addSMA(); addRSI()") 
```

### 6 Month Candle Stick Chart

```{r 6 Month candle stick chart, echo=FALSE, message=FALSE, warning=FALSE, comment=NA}
require(quantmod)

cat(("6 Month Candle Chart plus Technicals"),'\n')
candleChart(data,subset='last 6 months', multi.col=TRUE,theme='white',TA="addVo();addBBands();addEMA();addSMA(); addRSI()") 
```

## Statitiscal Analysis {.tabset}

### Statisitcal Summary of Historic Data
```{r hist summarize data, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, comment=NA}
require(Hmisc)
sumtable <- summary(data)
cat('Here are the summary statistics for the historical dataset:','\n')
cat('\n')
library(formattable)
formattable(sumtable)
write.table(sumtable, file=paste("/cloud/project/", stock, "_sumtable_", now,".txt", sep=""))
```

```{r hist boxplot, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
hist.bx <- as.data.frame(hist)
hist.boxplot <- boxplot(hist.bx$adjusted)
hist.boxplot
```

### Statisitcal Summary of YTD Data
```{r YTD summarize data, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, comment=NA}
require(Hmisc)
sumtable.ytd <- summary(ytd)
cat('Here are the summary statistics for the historical ytdset:','\n')
cat('\n')
library(formattable)
formattable(sumtable.ytd)
write.table(sumtable.ytd, file=paste("/cloud/project/", stock, "_sumtable_", now,".txt", sep=""))
```
```{r YTD boxplot, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
ytd.bx <- as.data.frame(ytd)
ytd.boxplot <- boxplot(ytd.bx$adjusted)
ytd.boxplot

ytd.bx <- cbind(date = rownames(ytd.bx), ytd.bx)
rownames(ytd.bx) <- 1:nrow(ytd.bx)

boxplot(ytd.bx$adjusted ~ ytd.bx$date,
data=ytd.bx,
main="Different boxplots for each month",
xlab="Month Number",
ylab="Price",
col="orange",
border="brown"
)
```

## Return Analysis {.tabset}

### Log Return YTD Data
```{r log return YTD data, echo=FALSE, message=FALSE, warning=FALSE, comment=NA, paged.print=FALSE}
log.return <- diff(log(ytd$adjusted))
log.return <- plot(log.return)
jpeg('log.return.jpg')
plot(log.return)
dev.off()
log.return
```

